\section{Chapter Overview}
The purpose of this chapter is to define the social, legal, ethical \& professional difficulties that may arise during the project, with steps taken to mitigate those issues.


\section{Breakdown of Social, Legal, Ethical and Professional Issues}

\vspace{-4mm}
\begin{longtable}{|p{0.473\linewidth}|p{0.473\linewidth}|}
\caption{Breakdown of SLEP Issues}\\ 
\hline
\textbf{Social} & \textbf{Legal} \endfirsthead 
\hline
\vspace{-7mm}       % remove line spacing before itemize
\begin{itemize}[leftmargin=*]
\item Questionnaire responses were not added to the thesis in a manner that would expose personal opinions of the respondents. Only the summary of responses were recorded.
\item Interviewers were notified that the responses will be recorded in the thesis \& their consent was taken to have their name \& designation added to the thesis.
\vspace{-7mm}       % remove line spacing after itemize
\end{itemize} & 
\vspace{-7mm}       % remove line spacing before itemize
\begin{itemize}[leftmargin=*]
\item All programming languages, tools \& frameworks that were used were under open source license.
\item All the source code of the research including data collection \& preprocessing will be licensed under GPL3 license.
\item The system was developed in a manner that no personal data would be required to produce the expected output.
\vspace{-7mm}       % remove line spacing after itemize
\end{itemize}
\\ 
\hline

\textbf{Ethical} & \textbf{Professional} \\ 
\hline
\vspace{-7mm}       % remove line spacing before itemize
\begin{itemize}[leftmargin=*]
\item Participants who completed the questionnaires were informed about the project and how they were contributing to it.
\item There is no fabrication, falsification, or plagiarism in the thesis. All of the data and information given are authentic, and the knowledge and facts that were retrieved were appropriately cited and referenced.
\vspace{-7mm}       % remove line spacing after itemize
\end{itemize}
& 
\vspace{-7mm}       % remove line spacing before itemize
\begin{itemize}[leftmargin=*]
\item None of the software or tools utilized to create the prototype were illegal or pirated. Only open source or student licenses were used throughout the process.
\item The project's outcomes were true to nature and were documented exactly as they were without any modifications.
\item A high level of research standards were followed throughout the research process.
\vspace{-7mm}       % remove line spacing after itemize
\end{itemize}
\\
\hline
\end{longtable}


\section{Chapter Summary}
This chapter identified possible social, legal, ethical \& professional issues under each section with mitigation strategies that were followed for the research.