% supervisor: Guhanathan Poravi sir
% evaluators, academic experts - for evaluation & guidance
% management & lecturers at IIT - for opportunities, support & guidance to get the knowledge I needed.
% friends from uni - I doubt I woul've been half the developer/ researcher I am today without their continued support and positive peer-pressure 
% ------
% parents - support & encouragement to pursue my dreams
% family & friends from school - for encouragement through tough times
% ---------
I had many people in my life that enabled me to go above and beyond what I used to be capable of to get to where I am today and successfully complete this final year research project.

I would first and foremost like to that my supervisor, Mr. Guhanathan Poravi sir for pushing me beyond my limits and showing me the best possible path of conducting research. Thanks to him, I have the confidence that I have the capability of conducting research at any level. I would like to thank the evaluators of this project who spent their precious time going through the work I had done and for giving advice on how I can improve my work at the ideation stage, the requirement gathering stage as well as the final evaluation stage of this research. This includes industry \& academia experts as well as all high-performing seniors \& juniors of IIT. I would specifically like to mention Nisal Sudila, Dilum De Silva, Mohamed Ayoub \& Chamath Palihawadana who haven't been mentioned/ taken part as evaluators, but have helped me shape my path at important cornerstones of the project as well as my undergraduate degree.

I would like to thank all the lecturers at the Informatics Institute of Technology as well as the management for the opportunities, support \& guidance they presented me with throughout my undergraduate degree. I would like to mention my friends from uni here, as I may not have been able to become half the developer/ researcher I am today if not for their continued support \& positive peer pressure. They have enabled me to grow exponentially fast over the course of 4 years. Finally, I would like to thank my parents for their support \& encouragement to pursue my dreams and my family \& friends from school for the encouragement shown toward me through tough times.